plackett_luce_monster

### 2022-07-15 inst/plackett_luce_monster.Rmd
generalized generalized Plackett-Luce

>>>>

# Five nations championship

The five nations rugby championship was held from 1910 to 1999 and
file five_nations.txt` shows the order statistic for England (E),
Scotland (S), Ireland (I), Wales (W), and France (F).

`https://en.wikipedia.org/wiki/Six_Nations_Championship`

Here is `hyper2` analysis:

```{r,load5nationsdata,cache=TRUE}
a <- as.matrix(read.table("five_nations.txt",header=FALSE))
head(a)
H <- hyper2()
for(i in seq_len(nrow(a))){
  H <- H + race(a[i,-1])
} 
mH <- maxp(H)
pie(mH)
equalp.test(H)
```

Now use `hyper3` to see whether teams do better following a win:

```{r,rugby3,cache=TRUE}
rugby <- function(lambda){
  H3a <- hyper3()
  for(i in seq(from=2,to=nrow(a))){
        last_year_winner <- a[i-1,2] # e.g. "W" or "E"
        H3a <- H3a + ordervec2supp3a(a[i,-1],nonfinishers=NULL,helped=last_year_winner,lambda=lambda)
  }
  return(H3a)
}
rugby(1.888)
rugby(1.111111)
```

```{r,rugby3max, cache=TRUE}
maxp(rugby(1.8),n=1,give=TRUE)
maxp(rugby(1.9),n=1,give=TRUE)
```
